Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-04-03 parts/summary.tex
adding comments about SW57, fixes #25

Figure~\ref{fig:stelmass} is another summary.  It shows most of the
candidates having stellar and total mass typical of massive
ellipticals.  SW05 is one of the most massive of all the candidates, with a
mass of galaxy-group scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it is a large system
with clear multiple-image features, and modelling leaves little doubt
that it is a lens.
SW04 seems to be even more massive, but the diagnostics leave some doubts
about this model.
The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, because of their low mass.
The models in both cases are plausible but not entirely satisfactory.
Their follow up, especially the one on SW42, would either confirm that
abundance matching and the halo-matching index $\haloindex$ are good
criteria for filtering possible candidates or it would lead to a really
interesting new, very low mass galaxy that is highly dominated by dark matter.

>>>>

Figure~\ref{fig:stelmass} is another summary.  It shows most of the
candidates having stellar and total mass typical of massive
ellipticals.  SW05 is one of the most massive of all the candidates, with a
mass of galaxy-group scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it is a large system
with clear multiple-image features, and modelling leaves little doubt
that it is a lens.
SW04 seems to be even more massive, but the diagnostics leave some doubts
about this model.
The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, as they would be low-mass lenses dominated 
by dark matter.  All the modelled systems have reasonable stellar-mass 
fractions, except for two cases where the stellar-mass fraction is too low 
(halo-matching index $>1$): these are SW42 and SW57.  In the case of SW57, the 
model has poor diagnostics and should be discounted.  The model for SW42, on the 
other hand, is quite convincing --- except for the high halo-matching index.  
If SW42 turns out not to be a lens, that would support the halo-matching index 
as an effective criterion for filtering models.
